Convolutional Neural Network to Detect Equivalent Questions in Online Forums \\ DL-IC 2018 Project

### 2018-07-13 paper/paper_final.tex
modified conclusion paper

\paragraph{Results and discussion.}
The experimental results show that the \emph{max} approach provides the best performances. This is probably due to the fact that the \emph{mean} approach is very likely to drop important semantic information from the sentence. However, it is worth mentioning that, in order for the \emph{max} approach to perform at its best, it is  definitely a good choice dropping the outliers, i.e. the questions that are too long with respect to the other observations. Figure \ref{fig:lens} shows the distribution of the question lengths of our dataset: it is evident that more than 95\% of the questions contains less than 400 words. Hence, we decide to drop the remaining 5\% of the questions.\\
In Figure \ref{fig:wiki} is represented the validation accuracy resulted from different combinations of hyperparameters values. For the sake of clarity we show in the figure only the best $cl_{u}$ value for each window size, but we observe that increasing too much the number of units of the convolutional layer, $cl_{u}$, provides worst performances.  As the figure indicates, smaller window sizes, provides the best performances.\\
Figure \ref{fig:embeddings} shows that, the addition of a trainable embedding layer, provides a performance improvement of around 1\%. The figure also highlights that (as stated in Table \ref{table:accuracy}) the model trained with in-domain embeddings outperform that trained using Wikipedia's embeddings.\\
The best model possible is, therefore, the CNN Multi-Channel initialized using in-domain word embeddings with $cl_u=300$ and $k=2$. It achieves 89\% accuracy on the test set.
\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Word embedding & Validation accuracy \\
\hline
Wikipedia & 86\% \\
AskUbuntu & 90\% \\
AskUbuntu multichannel & ??\% \\
\hline
\end{tabular}
\end{center}
\caption{Validation Accuracy with word embedding pretrained on different corpora.}
\label{table:accuracy}
\end{table}
\begin{figure}[t]
\begin{center}
\includegraphics[width=90mm, height= 55mm, scale=1]{img/Histogram.png}
\end{center}
\caption{Distribution of question lengths.}
\label{fig:lens}
\end{figure}
\begin{figure}[t]
\begin{center}
\includegraphics[width=90mm, height= 55mm, scale=1]{img/wiki.png}
\end{center}
\caption{Validation accuracy depending on the hyperparameters.}
\label{fig:wiki}
\end{figure}
\begin{figure}[t]
\begin{center}
\includegraphics[width=90mm, height= 55mm, scale=1]{img/embeddings_accuracy.png}
\end{center}
\caption{Validation Accuracy using Wikipedia's embeddings, AskUbuntu embeddings and CNN Multi-channel}
\label{fig:embeddings}
\end{figure}

\section{Conclusion} 
This work attempts to replicate the Bogdanova et al.' paper \cite{bogdanova2015detecting}. The obtained results are very close to our target. The in-domain word embeddings perform better than general-ones. The \emph{max} approach results to be the best solution for the problem of unequal text lengths. The CNN Multi-channel model brings a performance improvement of 1\%. The final model achieves 89\% accuracy on the test set.\\
A possible extension of this work could be to use an LSTM approach to solve the problem of unequal text lengths. Moreover, other deeper architectures could be explored.

>>>>

\paragraph{Results and discussion.}
The experimental results show that the \emph{max} approach provides the best performances. This is probably due to the fact that the \emph{mean} approach is very likely to drop important semantic information from the sentence. However, it is worth mentioning that, in order for the \emph{max} approach to perform at its best, it is  definitely a good choice dropping the outliers, i.e. the questions that are too long with respect to the other observations. Figure \ref{fig:lens} shows the distribution of the question lengths of our dataset: it is evident that more than 95\% of the questions contains less than 400 words. Hence, we decide to drop the remaining 5\% of the questions.\\
In Figure \ref{fig:wiki} is represented the validation accuracy resulted from different combinations of hyperparameters values. For the sake of clarity we show in the figure only the best $cl_{u}$ value for each window size, but we observe that increasing too much the number of units of the convolutional layer, $cl_{u}$, provides worst performances.  As the figure indicates, smaller window sizes, provides the best performances.\\
Figure \ref{fig:embeddings} shows that, the addition of a trainable embedding layer, provides a performance improvement of around 1\%. The figure also highlights that (as stated in Table \ref{table:accuracy}) the model trained with in-domain embeddings outperform that trained using Wikipedia's embeddings.\\
The best model possible is, therefore, the CNN Multi-Channel initialized using in-domain word embeddings with $cl_u=300$ and $k=2$. It achieves 89\% accuracy on the test set.
\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Word embedding & Validation accuracy \\
\hline
Wikipedia & 86\% \\
AskUbuntu & 90\% \\
AskUbuntu multichannel & 91\% \\
\hline
\end{tabular}
\end{center}
\caption{Validation Accuracy with word embedding pretrained on different corpora.}
\label{table:accuracy}
\end{table}
\begin{figure}[t]
\begin{center}
\includegraphics[width=90mm, height= 55mm, scale=1]{img/Histogram.png}
\end{center}
\caption{Distribution of question lengths.}
\label{fig:lens}
\end{figure}
\begin{figure}[t]
\begin{center}
\includegraphics[width=90mm, height= 55mm, scale=1]{img/wiki.png}
\end{center}
\caption{Validation accuracy depending on the hyperparameters.}
\label{fig:wiki}
\end{figure}
\begin{figure}[t]
\begin{center}
\includegraphics[width=90mm, height= 55mm, scale=1]{img/embeddings_accuracy.png}
\end{center}
\caption{Validation Accuracy using Wikipedia's embeddings, AskUbuntu embeddings and CNN Multi-channel}
\label{fig:embeddings}
\end{figure}

\section{Conclusion}

In this paper, we attempts to replicate the Bogdonova et al. paper \cite{bogdanova2015detecting} that propose a method for identifying semantically equivalent questions based on a convolutional neural network. 
We solve the problem of unequal text legths by considering the \emph{max} length, which reaches better performance with respect to the mean approach. We experimentally show that the proposed CNN achieves high accuracy especially when the word embeddings are pre-trained on in-domain data. In particular we found out that the CNN Multi-channel model brings a performance improvement of one-percent with respect to the model with only one matrix of word embeddings . This model achieves 89\% accuracy on the test set, that is a result very close to the one of our target.\\
A possible extension of this work could be to use an LSTM approach to solve the problem of unequal text lengths. Moreover, other deeper architectures could be explored.
